### 2015-03-18 ThesisJo/derivations.tex
la2pdf commit - 2015:03:18	15:51:13	(Wed18.Mar)

>>>>

\subsection{Oversampling and steering}

Steering wildly is not a good idea.

Too much steering, beamformer becomes too agressive. Uncertainty in source amplitude grows.

\begin{itemize}
\item More steering -> more aggressive suppression of interference at the cost of boosted sidelobes / noise.
\item More steering -> Larger variations in amplitude of sources
\end{itemize}

Idea to steer within a fraction of the rectangular window's mainlobe.

\begin{align*}
d = \frac{\pi\,\theta_\text{open}\,\lambda}{M\,d\,O_s}
\end{align*}

HISAS1030:
\begin{itemize}
\item 25$^\circ$ opening angle.
\item M$=32$ elements.
\item 
\end{itemize}

- Retain source amplitude
- Retain speckle statistics
- Improve resolution
- Easy to use

Skifte til 1/4 av bredden
